Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-14 article.qmd
Remove RateLaw comment
Rate law is an experimental law i.e. it is based on observations. On the other hand, law of mass action is a theoretical law based on the balanced chemical reaction.
Remove number of figure comment
For the application note it should be 2600 words,
or 2000 words plus 1 figure.

We have:
- 2914 words in total
- 2493 (-421) excluding references
- 2294 (-199) excluding code snippets
- 1947 (-347) excluding figure captions

For the reaction networks,
our focus is on first-order differential equations
that describe the rate of change of species.
SimBio simplifies the definition of these network models by introducing `Species`,
which consists of a `poincare.Variable` and stoichiometry,
and `Reaction`,
a construct that converts reactants into products taking into account the stoichiometry (@fig-simbio).
Additionally, SimBio features `MassAction`, a subclass of `Reaction`,
which intuitively incorporates reactants into the rate law (@fig-simbio).
**TODO: is `RateLaw` not better term than `MassAction`?**

@@

**TODO: I amnto sure whether the number of figures are already over the limit, you may have to combine figures, while doing so, if space permits create a small schematics / summary figure, with icons and texts showing the significance / and applicability of the tools developed.**

>>>>

For the reaction networks,
our focus is on first-order differential equations
that describe the rate of change of species.
SimBio simplifies the definition of these network models by introducing `Species`,
which consists of a `poincare.Variable` and stoichiometry,
and `Reaction`,
a construct that converts reactants into products taking into account the stoichiometry (@fig-simbio).
Additionally, SimBio features `MassAction`, a subclass of `Reaction`,
which intuitively incorporates reactants into the rate law (@fig-simbio).

@@
